some title

### 2018-01-07 2018/paper.tex
minor upd

The final step is to put everything together.
Note that since $y - \hat y$ is perpendicular to $Lin(x, \mathbf{1})$ it is also perpendicular to $\hat y - \bar y$ and $\mathbf{1}$ as these vectoros are in $Lin(x, \mathbf{1})$.
Then, applying the theorem of three perpendiculars we conclude that the foot of vector $y - \bar y$ is the same point as the foot of the vector $\hat y - \bar y$.
Thus, we obtain a right angle triangle and can apply the Pythagorean theorem for the catheti $\sqrt{RSS}$ and $\sqrt{ESS}$ and the hypothenuse $\sqrt{TSS}$:
\[
\sqrt{RSS} + \sqrt{ESS} = \sqrt{TSS}
\]

>>>>

The final step is to put everything together.
Note that since $y - \hat y$ is perpendicular to $Lin(x, \mathbf{1})$ it is also perpendicular to $\hat y - \bar y$ and $\mathbf{1}$ as these vectoros are in $Lin(x, \mathbf{1})$.
Then, applying the theorem of three perpendiculars we conclude that the foot of vector $y - \bar y$ is the same point as the foot of the vector $\hat y - \bar y$.
Thus, we obtain a right angle triangle and can apply the Pythagorean theorem for the catheti $\sqrt{RSS}$ and $\sqrt{ESS}$ and the
hypotenuse $\sqrt{TSS}$:
\[
(\sqrt{RSS})^2 + (\sqrt{ESS})^2 = (\sqrt{TSS})^2
\]
